\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-03-05 write_up/mixfishsim_ecolmod.tex
Manuscript changes to incorporate scenario runs

\begin{equation*}
	\begin{split}
	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
	     R \sim & N[(\bar{R},\sigma^2)]
	\end{split}
\end{equation*}
\textcolor{red}{[better to use lognormal variability to avoid negative
	recruitment events at low biomasses.]} Where $\alpha$ is the maximum
recruitment rate, $\beta$ the spawning stock biomass (SSB) required to produce
half the maximum, and $B$ current SSB; \\

@@

\begin{equation*}
	\begin{split}
	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
   	     R \sim & N[(\bar{R},\sigma^2)]
	\end{split}
\end{equation*}

@@

To simulate how fish populations might be distributed in space and time, we
employed a Gaussian spatial process to model habitat suitability for each of
the populations, with an advection-diffusion process to control how the
populations moved over time. \textcolor{red}{[say why - balance between realism
	and practicalities of IBMs for the fish population]}\\

@@

In the simulation model, the habitat for each of the populations is generated
through the \textit{RFSimulate} function of the \textit{RandomFields} R package
\cite{Schlater2015}, implementing different parameter settings to affect the
patchiness of the populations. Each population is initialised at a single
location, and subsequently moves according to a probabilistic distribtion based
on habitat suitability and distance from current cell.

\begin{equation}
	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
		Hab_{B}^2}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		Hab_{B}^2}
\end{equation}

Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
$\lambda$ is a given rate of decay and $Hab_{B}^2$ is the squared index of
habitat suitability for cell $B$.\\

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of ... \textcolor{red}{[expand]}. To do so, we first set up with
simulation to run for 20 years based on a 100 X 100 square grid, with five
fleets of 20 vessels each and four fish populations. Fishing takes place four
times a day per vessel and five days a week, while population movement is every
week.

@@

>>>>

\begin{equation*}
	\begin{split}
	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
	\end{split}
\end{equation*}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum, $B$ current SSB and
$\sigma^2$ the variability in the recruitment due to stochastic
processes. \\

@@

\begin{equation*}
	\begin{split}
	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
   	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
	\end{split}
\end{equation*}

@@

To simulate how fish populations might be distributed in space and time, we
employed a Gaussian spatial process to model habitat suitability for each of
the populations, with an advection-diffusion process to control how the
populations moved over time with a moving temperature covariate to capture
temporal dependencies. This was intended to balance realism in population
movement, capturing the main directed and random processes, and practicality of
modelling the population rather than individual fish. \\

@@

The temperature field is simulated to be on a gradient from a South-Westerly to
North-Easterly direction, with temperature in each cell changing gradually on a
week-by-week basis so that initially high temperature areas cycle to lower
temperatures and low temperature areas vice versa. Each population is assigned
a thermal tolerance with mean, $\mu$ and variance, $\sigma^2$ so that each cell
and population temperature suitability is defined that:

\begin{equation}
	Tol_{c, p} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c} -
		\mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}

Where $Tol_{c,p}$ is the tolerance of population $p$ in cell $c$, $T_{c}$ is
the temperature in the cell and $\mu$ and $\sigma^2$ the mean and standard
deviation of the population temperature tolerance. \\

In the simulation model, the habitat for each of the populations is generated
through the \textit{RFSimulate} function of the \textit{RandomFields} R package
\cite{Schlater2015}, implementing different parameter settings to affect the
patchiness of the populations. Each population is initialised at a single
location, and subsequently moves according to a probabilistic distribtion based
on habitat suitability, temperature and distance from current cell.

\begin{equation}
	Pr(B | A) = \frac{e^{-\lambda * d_{AB}} \cdot
		(Hab_{B}^2 \cdot Tol_{B,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{B}^2 \cdot Tol_{B,wk})}
\end{equation}

Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$,
$\lambda$ is a given rate of decay, $Hab_{B}^2$ is the squared index of habitat
suitability for cell $B$ and $Tol_{B,wk}$ the temperature tolerance for the
cell in week $wk$; population index, $p$ has been dropped for simplicity.\\

@@

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
first set up with simulation to run for 10 years based on a 100 X 100 square
grid, with five fleets of 20 vessels each and four fish populations. Fishing
takes place four times a day per vessel and five days a week, while population
movement is every week. \\

We allow the simulation to run unrestricted for 5 years, and subsequently close
areas for the last 5 years of the simulation based on data (either derived from
the commercial catches, fisheries-independent survey or the 'real population')
used at different spatial and temporal scales.

The following steps are undertaken to determine closures:

i. Extract data source
ii. Aggregate according to resolution
iii. Interpolate across entire area at desired resoltion
iv. Close top 5 \% of areas

\begin{table}[!ht]
\caption{Closure scenarios}
\begin{tabular}{ p{4cm } p{4cm} p{4cm}}
	\hline
	Data type & Temporal resolution & Spatial resolution \\
	\hline
	Commercial logs, survey data, real population & weekly, monthly, years
	& 1, 2, 5, 10 \\ 
\end{tabular}
\label{tab:x}
\end{table}

ABOVE WOULD BE BETTER AS SOME SORT OF GRAPHICAL ILLUSTRATION OF AGGREGATION
CONSEQUENCES, E.G. 
COMMERCIAL DATA SPARSITY, SURVEY DATA CONSISTENCY, REAL
POPULATION IS ALL.

TEMPORALLY VARYING PROPORTIONS DIVIDED BY WEEK, MONTH, YEAR

CELLS AGGREGATED ACCORDING TO SIMULATION EXAMPLES !!!

Total 56 scenarios.
